---
title: "Ant Trophallaxis Modeling - Colony 2"
author: Meridith L. Bartley
output: html_notebook
---

The purpose of this notebook is to document the analysis and visualisation of Colony 2. 

```{r}
library(magrittr)
library(ggplot2)
library(dplyr)
library(doMC)
```



```{r call in data, include=FALSE}

#data directory
dat.dir <- "../data-raw/"

#output directory
out.dir <- "../output/"


#column names - helps when only pulling in those columns, no extra

col_names <- c("Location", "Ant_ID", "Ant_ID_partner", "start_time", "end_time")


col2_high4 <- read.csv("../data-raw/Colony2_trophallaxis_high_density_4hr.csv")
col2_low4 <- read.csv("../data-raw/Colony2_trophallaxis_low_density_4hr.csv")

#removes any extra columns, rows, and adds column names - depends on col_names being correct length
col2_high4 <- col2_high4[, 1:length(col_names)]
col2_high4 <- col2_high4 %>% 
            tidyr::drop_na()
colnames(col2_high4) <- col_names

col2_low4 <- col2_low4[, 1:length(col_names)]
col2_low4 <- col2_low4 %>% 
            tidyr::drop_na()
colnames(col2_low4) <- col_names

#check for correct class for data (numberic, etc)


```

#Exploratory Data Analysis

An important basis for this model is the 'pulses' of interactions seen over time. We want to explore each chamber where interactions take place. 


```{r data visualization, include=FALSE}


sumvis_high <- sumvis_troph(data = col2_high4, entrance = F, hours = 4, density = "high")


sumvis_low <- sumvis_troph(data = col2_low4, entrance = F, hours = 4, density = "low")


```

We can see from these graphs for the high density colony data that on average for a four hour span of time ants engage in `r round(mean(sumvis_high$all.ID), 1)` interactions per ant for `r sumvis_high$allants` ants. In total, `r sum(sumvis_high$all.ID)/2 ` interactions occured within the single chamber. 

For the low density colony data, there was an average of `r round(mean(sumvis_low$all.ID), 1)` interactions per ant overall for all four chambers. In total, `r sum(sumvis_low$all.ID)/2 ` interactions occured within all chambers between `r sumvis_high$allants`.  




```{r prep interaction data, include=FALSE}

col2_high4_5 <- prep_troph_data(col2_high4, hours = 4, delta_t = 5)
col2_low4_5 <- prep_troph_data(col2_low4, hours = 4, delta_t =  5)
```


# Simple Model 

In order to showcase the improvements our Penalized Hidden Markov Model for colony level trophallaxis rates makes over other models, we first would like to run a simpler/less penelized version of our model on the ant data. This should serve to nicely exemplify the problem of overfitting our stochastic process. 

```{r all models}
# Variables needed for all 

path <- out.dir
path_table <- "../output/tables/" 
states <- 2
n_mcmc <- 10000
hours <- 4
X <- sample(x = c(1, 2), size = hours*60*60, replace = T)
lambda <- c(.01, .08)
# registerDoMC(cores = 5) 
```

We will run all models as 2-state HMM models, as determined by previous work. 

```{r simple model }
#parameters specific to simple model - no penalization
# theta <- matrix(data = c(5000, 1, 1, 5000), nrow = 2, ncol = 2, byrow = T) 
P <- matrix(c(.997, .003, .003, .997), nrow = 2, byrow = T)
param_start <- list(X = X, lambda = lambda, P = P)

#high density - one chamber


#low density - both chambers

#low density - queen's chamber -- USED FOR PAPER

simple_col2lo4qbin1 <- foreach(i = seq(23000, 25000, by =  1000) ,
                                .errorhandling = "remove") %dopar% 
                        DT_mcmc_troph(starts_data = col2_low4_5$queen_starts_persec, 
                                     ant_file = col2_low4_5$data, chamber = "queen", 
                                     title = "Test", 
                                     a = .005, b = .001, c = .005, d = .001, 
                                     theta = matrix(c(i, 1, 1, i), 2, 2), states = states, 
                                     n_mcmc = n_mcmc, delta_t = 1, hours = hours,
                                     param_start = param_start, fig_save = TRUE, 
                                     fig_path = path, fig_name = "simp_col2lo4qbin1", 
                                     plot_title = "test") 

#low density - entrance chamber


```

```{r}
sumtable_model(results = simple_col2lo4qbin1, compare = seq(23000, 25000, by =  1000), 
               file_path = path_table, 
               file_name = "test", model = "simple")



```




