---
title: "Ant Trophallaxis Modeling - Colony 1"
author: Meridith L. Bartley
output: html_notebook
---

The purpose of this notebook is to document the analysis and visualisation of Colony 2. 

```{r}
library(magrittr)
library(mvtnorm)
library(ggplot2)
library(gtools)
library(dplyr)
library(doMC)

options(error = recover)
```



```{r call in data, include=FALSE}

#data directory
dat.dir <- "../data-raw/"

#output directory
out.dir <- "../output/"


#column names - helps when only pulling in those columns, no extra

col_names <- c("Location", "Ant_ID", "Ant_ID_partner", "start_time", "end_time")


col1_high4 <- read.csv("../data-raw/Colony1_trophallaxis_high_density_4hr.csv")
col1_low4 <- read.csv("../data-raw/Colony1_trophallaxis_low_density_4hr.csv")

#removes any extra columns, rows, and adds column names - depends on col_names being correct length
col1_high4 <- col1_high4[, 1:length(col_names)]
col1_high4 <- col1_high4 %>% 
            tidyr::drop_na()
colnames(col1_high4) <- col_names

col1_low4 <- col1_low4[, 1:length(col_names)]
col1_low4 <- col1_low4 %>% 
            tidyr::drop_na()
colnames(col1_low4) <- col_names

#check for correct class for data (numberic, etc)


## call in covariate data 
load("../data-raw/Colony1_covariate_low_density_4hr.Rda")


```

#Exploratory Data Analysis

An important basis for this model is the 'pulses' of interactions seen over time. We want to explore each chamber where interactions take place. 


```{r data visualization, include=FALSE}


# sumvis_high <- sumvis_troph(data = col2_high4, entrance = F, hours = 4, density = "high")


sumvis_low <- sumvis_troph(data = col1_low4, entrance = F, hours = 4, density = "low")



```

We can see from these graphs for the high density colony data that on average for a four hour span of time ants engage in `r round(mean(sumvis_high$all.ID), 1)` interactions per ant for `r sumvis_high$allants` ants. In total, `r sum(sumvis_high$all.ID)/2 ` interactions occured within the single chamber. 

For the low density colony data, there was an average of `r round(mean(sumvis_low$all.ID), 1)` interactions per ant overall for all four chambers. In total, `r sum(sumvis_low$all.ID)/2 ` interactions occured within all chambers between `r sumvis_high$allants`.  




```{r prep interaction data, include=FALSE}

col2_high4_5 <- prep_troph_data(col2_high4, hours = 4, delta_t = 5)
col1_low4_5 <- prep_troph_data(col1_low4, hours = 4, delta_t =  5)
```


```{r prep covariate data, include = FALSE}
covariate.prepped <- prep_inout_data(covariate, delta_t = 1, hours = 4)

Time4 <- 4 * 60 * 60

location <- col1_low4_5$data$Location
start <- col1_low4_5$data$start_time
   # chamber <- chamber


start = start[which(location == 1)]
  

   start <- sort(start)
   int.num <- length(start)
   covariate <- covariate.prepped$cov
  
# pdf( file = "../output/Pen2CovPlot.pdf")
 
plot(start, 1:int.num, xlab = "Seconds", ylab = "Cumulative Interaction Count",
     xlim = c(0, Time4))
    points(which(covariate == 0), rep(0, length(which(covariate == 0))), pch = 8, col = "#53bc84")

# dev.off()



# cov_col2_low4 <- prep_inout_data(covariate, delta_t = 1, hours = 4)

```



# Simple Model 

In order to showcase the improvements our Penalized Hidden Markov Model for colony level trophallaxis rates makes over other models, we first would like to run a simpler/less penelized version of our model on the ant data. This should serve to nicely exemplify the problem of overfitting our stochastic process. 

```{r all models}
# Variables needed for all 

path <- out.dir
path_table <- "../output/tables/" 
states <- 2
# states <- 3
n_mcmc <- 40000
hours <- 4
X <- sample(x = c(1, 2), size = hours*60*60, replace = T)
X <- pen_results[[3]][-(1:9), 1]
X_3 <- sample(x = 1:3, size = hours * 60 * 60, replace = T)
lambda <- c(.007, .05)
 registerDoMC(cores = 1) 
```

We will run all models as 2-state HMM models, as determined by previous work. 

```{r simple model, eval=FALSE, include=FALSE}
#parameters specific to simple model - no penalization
# theta <- matrix(data = c(5000, 1, 1, 5000), nrow = 2, ncol = 2, byrow = T) 
P <- matrix(c(.997, .003, .003, .997), nrow = 2, byrow = T)
param_start <- list(X = X, lambda = lambda, P = P)
delta_t <- 1
#high density - one chamber


#low density - both chambers

#low density - queen's chamber -- USED FOR PAPER

i <- seq(120000, 120000, by =  2000)

  # RUN ONLY ONCE - DON'T RESAVE OVER DATA
  # write.csv(t(c(1, 2, 3, 4)),
  #           # col.names = c("Penalty", "MSPE", "Accept", "Number of Iterations"),
  #           file = "../output/modelsrun_sim2.csv")
  
  simple_col2lo4qbin1_21k <- #foreach(i = range_simple ,
                                  #.errorhandling = "remove") %dopar% 
                          DT_mcmc_troph(starts_data = col2_low4_5$queen_starts_persec, 
                                       ant_file = col2_low4_5$data, chamber = "queen", 
                                       title = "Test", 
                                       a = 1, b = 1, c = 1, d = 1, 
                                       theta = matrix(c(i, 1, 1, i), 2, 2), states = states, 
                                       n_mcmc = n_mcmc, delta_t = 1, hours = hours,
                                       param_start = param_start, fig_save = TRUE, 
                                        data_out = paste("../data/", "sim_MCMC", "-", 
                                                         (i), "-", n_mcmc, ".csv", sep = ""),                                            modelsrun_out = paste("../output/modelsrun_sim2.csv", sep="")) 

     #low density - entrance chamber


```

```{r compare simple, eval=FALSE, include=FALSE}

MSPE_results_simp2 <- read.csv("../output/modelsrun_sim2.csv")

MSPE_results_simp2 <- as.data.frame(MSPE_results_simp2[ which(MSPE_results_simp2$V3 >= 10000), -1] )
colnames(MSPE_results_simp2) <- c("penalty", "MSPE", "num_iter")

plot(MSPE_results_simp2$penalty, MSPE_results_simp2$MSPE)



# sumtable_model(results = simple_col2lo4qbin1, compare = range_simple, 
#                file_path = path_table, 
#                file_name = "test", model = "simple")


sim_results <- list()

# range <- exp(minMSPE[1]) #if only want one penalty that has been optimized
range_simple <- c( 120000)
 r <- 1

# range <- c(exp(minMSPE[1]), exp(maxMSPE[1]))
# range <- as.data.frame(range)

 for (r in 1:length(range_simple)) {
  

temp_results <-  readr::read_csv(paste("../data/sim_MCMC-",
                                (range_simple[r]), "-", n_mcmc,  
                                ".csv", sep = ""))
  delta_t <- 1
sim_results[[r]] <- penalty_diagnosis(t(temp_results)[-1, ], 
                                      states = 2, 
                                      ant_file = col2_low4_5$data, 
                                      chamber = "queen", 
                                      Time = hours * 60 * 60, fig_path = path,
                                fig_name = "Sim2_MSPE", penalty = (range_simple[r]))
 
}

 #also want to redo pen_diag for just latter half of iteratinos (manual removal of burn in)
 
 dim(t(temp_results)[-1, ])
 dim(t(temp_results)[-1,-(1:(n_mcmc/2))]) 
 
 sim_results[[2]] <-  penalty_diagnosis(t(temp_results)[-1, -(1:(n_mcmc/2))], 
                                      states = 2, 
                                      ant_file = col2_low4_5$data, 
                                      chamber = "queen", 
                                      Time = hours * 60 * 60, fig_path = path,
                                fig_name = "Sim2_MSPE_2ndhalf", penalty = (range_simple[r]))
 #want to use above to rerun model for another 40k iter
 
##compare estimates
 
 cbind(sim_results[[1]][1:7, ], sim_results[[2]][1:7, ]) #full set, just 2nd half
 
 
rm(temp_results)
```

#Penalized Model

```{r penalized model, eval=FALSE, include=FALSE}

tau <- matrix( c(.1, 0, 
                 0, .1), nrow = 2, ncol = 2)
gamma <- c(.0005, .0005) #NEXT: change to .0005 and rerun model at e^-23
start <- list(X = X, lambda = lambda, gamma = gamma) 
delta_t <- 1

# high density - one chamber

#low density - both chambers

#low densith - queen's chamber USED FOR PAPER

##THIS ONE FOR JSM
range <- exp(seq(-40, -22, by =  2))
range <- exp(-23)

penalize_col2lo4qbin1 <- foreach(i = range,
                                  .errorhandling = "remove") %dopar% 
  DT_pen_mcmc(penalty = i, starts_data = col2_low4_5$queen_starts_persec, 
              states = states, ant_file = col2_low4_5$data, chamber = "queen",
              hours = 4,
              a = 1, b = 1, c = 1, d = 1,
              tau = tau, tau.pen = 0, n_mcmc = n_mcmc, 
              delta_t = delta_t, start = start, 
              data_out = paste("../data/", "pen_MCMC", "-", 
                               log(i), "-", n_mcmc, ".csv", sep = ""), 
              osa_out = paste("../data/", "pen_OSA", "-", 
                               log(i), "-", n_mcmc, ".csv", sep = ""))



#low density - entrance chamber
```


```{r compare penalized, eval=FALSE, include=FALSE}

#previous results - don't want to save over!

   old_MSPE_results <- as.data.frame(MSPE_results)

Time = hours *60 *60

MSPE_results <- matrix(NA, ncol = 2, nrow = length(range))
  colnames(MSPE_results) = c("penalty", "MSPE")

for (r in 1:length(range)) {

  osa_param <-  readr::read_csv(paste("../data/pen_OSA-",
                                  log(range[r]), "-", n_mcmc,  
                                  ".csv", sep = ""))
  
  
  data <- col2_low4_5$queen_starts_persec
  
  data_mat <- matrix(rep(data, nrow(osa_param)), byrow = T, nrow = nrow(osa_param))
  
  sum.it <- sum((osa_param[, -1] - data_mat)^2)
  # square <- subtract^2
  # sum.it <- sum(square)
  

  MSPE.1SA <- 1/n_mcmc * 1/Time * sum.it


MSPE_results[r, 1] <- log(range[r])
MSPE_results[r, 2] <- MSPE.1SA
# MSPE_results[r, 3] <- penalize_col2lo4qbin1[[r]]$accept
}
  

  
  #remove useless stuff
  rm(data_mat)
  rm(final)
  rm(osa_param)

  
#combine with old data
  MSPE_results <- rbind(old_MSPE_results[, 1:2], MSPE_results)
  
MSPE_results <- as.data.frame(MSPE_results)
  
compare_plot <- ggplot(data = MSPE_results, aes(x = penalty, y = MSPE)) +
                  geom_point(aes(x = penalty)) 


minMSPE <- MSPE_results[which.min(MSPE_results$MSPE), ]

#out of curiosity
maxMSPE <- MSPE_results[which.max(MSPE_results$MSPE), ]


print(compare_plot)
print(compare_plot + ylim(.0177, .019)) #limits chosen via observation of first plot


plot_pen2 <- compare_plot + 
        geom_vline( xintercept=-23, col = 'red') + 
        xlab("Penalty (e^value)") + 
        xlim(-30, 30) +
        # theme_bw(base_size = 13, base_family = "Helvetica") + 
        theme(text = element_text(size=14),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(),
              # panel.background = element_blank(),
              axis.line = element_line(colour = "black")) 

print(plot_pen2)
ggsave("../output/MSPE_pen2.pdf")

#save MSPE_results
save(MSPE_results, file = "../output/MSPE_pen2_table.Rda")

```

```{r penalized diagnoses, eval=FALSE, include=FALSE}

pen_results <- list()

range <- exp(minMSPE[1]) #if only want one penalty that has been optimized
range <- exp(c( -6))
 r <- 1

range <- c(exp(minMSPE[1]), exp(maxMSPE[1]))
range <- as.data.frame(range)

 for (r in 1:length(range)) {
  

temp_results <-  readr::read_csv(paste("../data/pen_MCMC_3.0-",
                                log(range[r]), "-", 20000,  
                                ".csv", sep = ""))

pen_results[[r]] <- penalty_diagnosis(t(temp_results)[-1, ], 
                                      states = 2, 
                                      ant_file = col2_low4_5$data, 
                                      chamber = "queen", 
                                      Time = hours * 60 * 60, fig_path = path,
                                fig_name = "Pen2_MSPE", penalty = log(range[r]))
 
}


##how much of time is spent in High state?

length(which(round(pen_results[[1]][-(1:9), 1]) ==2))/(4 * 60 * 60)


rm(temp_results)

```

```{r penalized THREE model, eval=FALSE, include=FALSE}
tau <- matrix( c(.1, 0, 
                 0, .1), nrow = 2, ncol = 2)
gamma_3 <- rep(.002, 6)
lambda_3 <- c(0, 0.006, .05)
start_3 <- list(X = X_3, lambda = lambda_3, gamma = gamma_3) 
delta_t <- 1

# high density - one chamber

#low density - both chambers

#low densith - queen's chamber USED FOR PAPER

##THIS ONE FOR JSM
range_3 <- exp(seq(-30, -1, by =  1))
 i <- exp(-4)
 
# write.csv(t(c(1, 2, 3, 4)),
#           # col.names = c("Penalty", "MSPE", "Accept", "Number of Iterations"),
#           file = "../output/modelsrun_PCpen3.csv")

penalize3_col2lo4qbin1 <- foreach(i = range_3,
                                  .errorhandling = "remove") %dopar% 
  DT_pen_mcmc(penalty = i, starts_data = col2_low4_5$queen_starts_persec, 
              states = 3, ant_file = col2_low4_5$data, chamber = "queen",
              hours = 4,
              a = 1, b = 1, c = 1, d = 1, e = 1, f = 1, 
              tau = tau, tau.pen = 0, n_mcmc = n_mcmc, 
              delta_t = delta_t, start = start_3, 
              data_out = paste("../data/", "pen3_MCMC", "-", 
                               log(i), "-", n_mcmc, ".csv", sep = ""), 
              osa_out = paste("../data/", "pen3_OSA", "-", 
                               log(i), "-", n_mcmc, ".csv", sep = ""), 
               modelsrun_out = paste("../output/modelsrun_PCpen3.csv", sep=""), 
                          fig_path = path, fig_name = "PC_pen3_MCMC")



#low density - entrance chamber
```


```{r compare penalized THREE, eval=FALSE, include=FALSE}

#previous results - don't want to save over!

    old_MSPE_results_THREE <- as.data.frame(MSPE_results_THREE)

Time = hours *60 *60

MSPE_results_THREE <- matrix(NA, ncol = 2, nrow = length(range_3))
  colnames(MSPE_results_THREE) = c("penalty", "MSPE")

for (r in 1:length(range_3)) {

  osa_param <-  readr::read_csv(paste("../data/pen3_OSA-",
                                  log(range_3[r]), "-", n_mcmc,  
                                  ".csv", sep = ""))
  
  
  data <- col2_low4_5$queen_starts_persec
  
  data_mat <- matrix(rep(data, nrow(osa_param)), byrow = T)
  
  sum.it <- sum((osa_param[, -1] - data_mat)^2)
  # square <- subtract^2
  # sum.it <- sum(square)
  

  MSPE.1SA <- 1/n_mcmc * 1/Time * sum.it


MSPE_results_THREE[r, 1] <- log(range_3[r])
MSPE_results_THREE[r, 2] <- MSPE.1SA
# MSPE_results[r, 3] <- penalize_col2lo4qbin1[[r]]$accept
}
  

  
  #remove useless stuff
  rm(data_mat)
  # rm(final)
  rm(osa_param)

  
#combine with old data
  MSPE_results_THREE <- rbind(old_MSPE_results_THREE[, 1:2], MSPE_results_THREE)
  
MSPE_results_THREE <- as.data.frame(MSPE_results_THREE)
  
compare_plot_3 <- ggplot(data = MSPE_results_THREE, aes(x = penalty, y = MSPE)) +
                  geom_point(aes(x = penalty)) 


minMSPE_3 <- MSPE_results_THREE[which.min(MSPE_results_THREE$MSPE), ]

#out of curiosity
maxMSPE_3 <- MSPE_results_THREE[which.max(MSPE_results_THREE$MSPE), ]


print(compare_plot_3)

plot_pen3 <- compare_plot_3 + 
        ylim(.0185, .0188) + 
            geom_vline( xintercept=-13, col = 'red') + 
        xlab("Penalty (e^value)") + 
        xlim(-30, 10) +
        # theme_bw(base_size = 13, base_family = "Helvetica") + 
        theme(text = element_text(size=14),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(),
              # panel.background = element_blank(),
              axis.line = element_line(colour = "black"))  #limits chosen via observation of first plot

print(plot_pen3)

ggsave("../output/MSPE_pen3.pdf")

save(MSPE_results_THREE, file = "../output/MSPE_pen3_table.Rda")


```

```{r penalized THREE diagnoses, eval=FALSE, include=FALSE}

pen3_results <- list()
delta_t <- 1

range_3 <- exp(minMSPE_3[1]) #if only want one penalty that has been optimized
range_3 <- exp(-3)
 r <- 1

range_3 <- c(exp(minMSPE_3[1]), exp(maxMSPE_3[1]))
range_3 <- as.data.frame(range_3)

 for (r in 1:length(range_3)) {
  

temp_results <-  readr::read_csv(paste("../data/pen3_MCMC_2.0-",
                                log(range_3[r]), "-", 40000,  
                                ".csv", sep = ""))

pen3_results[[r]] <- penalty_diagnosis(t(temp_results[, -1 ]), 
                                      states = 3,
                                      ant_file = col2_low4_5$data, 
                                      chamber = "queen", 
                                      Time = hours * 60 * 60, fig_path = path,
                                fig_name = "MSPE3", penalty = log(range_3[r]))
 
}

 
pen3_results[[1]] <-  penalty_diagnosis(t(temp_results[ -(1:10000), -1 ]), 
                                      states = 3,
                                      ant_file = col2_low4_5$data, 
                                      chamber = "queen", 
                                      Time = hours * 60 * 60, fig_path = path,
                                fig_name = "MSPE3_2ndhalf_diffcol3", penalty = log(range_3[r]))
 

#what % in medium state
length(which(round(pen3_results[[1]][-(1:19), 1]) ==2))/(4 * 60 * 60)

#what % in high state
length(which(round(pen3_results[[1]][-(1:19), 1]) ==3))/(4 * 60 * 60)



#want to use above to rerun model for another 40k iter
 
##compare estimates
 
 cbind(pen3_results[[1]][1:19, ], pen3_results[[2]][1:19, ]) #full set, just 2nd half
 
 est3 <- as.data.frame(pen3_results[[2]][1:19, ]) %>% mutate(LB = est - 2* se, UB = est + 2 * se)
round(est3, 4)

 
rm(temp_results)

```


#Penalty Covariate Model

```{r pencov ant data 2state}

 tau <- matrix( c(.001, 0, 0, 0, 0,
                  0, .001, 0, 0, 0,
                  0, 0, .01, 0, 0,
                  0, 0,  0, .000000005, 0, 
                  0, 0, 0, 0, .001), nrow = 5, ncol = 5)
betas <- c(.0004, .4, .0004, 0, .25)
start <- list(X = X, lambda = lambda, betas = betas)
delta_t <- 1

range_pencov <- exp(seq(-5, -1, by =  1))

i <- range_pencov[3]
# write.csv(t(c(1, 2, 3, 4)),
#           col.names = c("Penalty", "MSPE", "Accept", "Number of Iterations"),
#           file = "../output/modelsrun_testpencov.csv")


pencov_col2lo4qbin1 <- foreach(i = range_pencov,
                                  .errorhandling = "remove") %dopar% 
  DT_pencov_MCMC(penalty = i, starts_data = col2_low4_5$queen_starts_persec, 
              states = states, ant_file = col2_low4_5$data, chamber = "queen",
              hours = 4,
              a = 1, b = 1, c = 1, d = 1,
              tau = tau, tau.pen = 0, n_mcmc = n_mcmc, 
              delta_t = delta_t, start = start, 
              data_out = paste("../data/", "pencov_MCMC", "-", 
                               log(i), "-", n_mcmc, ".csv", sep = ""), 
              osa_out = paste("../data/", "pencov_OSA", "-", 
                               log(i), "-", n_mcmc, ".csv", sep = ""), 
              modelsrun_out = paste("../output/modelsrun_testpencov.csv", sep=""), 
              fig_path = path, fig_name = "pencov_MCMC",
              covariate = (covariate.prepped$cov ))
                           # - mean(cov_col2_low4$cov))/10)


```

```{r pencov 2 state OSA calc }

#previous results - don't want to save over!

#      old_MSPE_results_cov <- as.data.frame(MSPE_results_cov)
# 
# Time = hours *60 *60
# 
# MSPE_results_cov <- matrix(NA, ncol = 2, nrow = length(range_pencov))
#   colnames(MSPE_results_cov) = c("penalty", "MSPE")
# 
# for (r in 1:length(range_pencov)) {
# 
#   osa_param <-  readr::read_csv(paste("../data/pencov_OSA-",
#                                   log(range_pencov[r]), "-", n_mcmc,  
#                                   ".csv", sep = ""))
#   
#   
#   data <- col2_low4_5$queen_starts_persec
#   
#   data_mat <- matrix(rep(data, nrow(osa_param)), byrow = T)
#   
#   sum.it <- sum((osa_param[, -1] - data_mat)^2)
#   # square <- subtract^2
#   # sum.it <- sum(square)
#   
# 
#   MSPE.1SA <- 1/n_mcmc * 1/Time * sum.it
# 
# 
# MSPE_results_cov[r, 1] <- log(range_pencov[r])
# MSPE_results_cov[r, 2] <- MSPE.1SA
# # MSPE_results[r, 3] <- penalize_col2lo4qbin1[[r]]$accept
# }
#   
# 
#   
#   #remove useless stuff
#   rm(data_mat)
#   # rm(final)
#   rm(osa_param)
# 
#   
# #combine with old data
#   MSPE_results_cov <- rbind(old_MSPE_results_cov[, 1:2], MSPE_results_cov)

MSPE_results_cov <- readr::read_csv(paste("../output/modelsrun_testpencov.csv"))

  
MSPE_results_cov <- as.data.frame(MSPE_results_cov[which(MSPE_results_cov$V4 >= n_mcmc), -1])
colnames(MSPE_results_cov) <- c("penalty", "MSPE", "accept", "numiter")

  
compare_plot_cov <- ggplot(data = MSPE_results_cov, aes(x = penalty, y = MSPE)) +
                  geom_point(aes(x = penalty)) 


minMSPE_cov <- MSPE_results_cov[which.min(MSPE_results_cov$MSPE), ]

#out of curiosity
maxMSPE_cov <- MSPE_results_cov[which.max(MSPE_results_cov$MSPE), ]


print(compare_plot_cov)

plot_pencov <- compare_plot_cov + 
        ylim(.0184, .01865) + 
            geom_vline( xintercept= - 29, col = 'red') + 
        xlab("Penalty (e^value)") + 
        xlim(-30, 10) +
        # theme_bw(base_size = 13, base_family = "Helvetica") + 
        theme(text = element_text(size=14),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(),
              # panel.background = element_blank(),
              axis.line = element_line(colour = "black"))  #limits chosen via observation of first plot

print(plot_pencov)

ggsave("../output/MSPE_pencov.pdf")

save(MSPE_results_cov, file = "../output/MSPE_pencov_table.Rda")

```

```{r penalized covariate diagnoses, eval=FALSE, include=FALSE}
delta_t <- 1
pencov_results <- list()
# 
# range_pencov <- exp(minMSPE_cov[1]) #if only want one penalty that has been optimized
r <- 1
# 
# range_pencov <- c(exp(minMSPE_cov[1]), exp(maxMSPE_cov[1]))
range_pencov <- c(exp(-3))
range_pencov <- as.data.frame(range_pencov)

 for (r in 1:length(range_pencov)) {
  

temp_results <-  readr::read_csv(paste("../data/pencov_MCMC-",
                                log(range_pencov[r]), "-", n_mcmc,  
                                ".csv", sep = ""))

pencov_results[[r]] <- penalty_diagnosis(t(temp_results[, -1 ]), 
                                      states = 2,
                                      ant_file = col2_low4_5$data, 
                                      chamber = "queen", 
                                      Time = hours * 60 * 60, fig_path = path,
                                fig_name = "MSPEcov", penalty = log(range_pencov[r]), 
                                covariate = covariate.prepped$cov)
 
}


 est_cov <- as.data.frame(pencov_results[[1]][1:15, ]) %>% mutate(LB = est - 2* se, UB = est + 2 * se)
round(est_cov, 5)

rm(temp_results)

```
